Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-28 journal/article.tex
Work in progress

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Type of leading change         &  Described in  \\
        \midrule
        Agile task group foor coordinating change   &
                P4, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Which entities were leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

Many organizations formed an agile task force or similar entity for coordinating
and leading the change. It was typical that in the beginning of the
transformation, or when it had been acknowledged that the old model had
problems, a work group was founded for coordinating the changes to be done. The
change team usually consisted of management personnel [P43, P50], and was
reinforced with external agile consultants [P18, P21, P25, P30]. Some cases
highlighted that the team had a cross organizational staff who were familiar
with the varying functions that would be affected by changes [P4, P21, P41,
P48]. It was important that theere was a group of people who were strongly
committed to making a change happen [P43].

The tasks of the change team included first finding an alternative delivery
method to solve problems in the old model [P21, P30]. During the transformation
the team stimulated agile adoption in the organization [P18, P45, P49]. Examples
on their tasks were informing people on the agile model [P4], educating and
coaching [P45, P48, P49], creating an agile cookbook [P23], and organizing
presentations and workshops [P25, P41]. The change team also assessed the
success of transformed teams, and worked for repeating their success across the
organization [P40, P41].
% The team was also empowered to remove the impediments they discovered [P50].

@@

@@

>>>>

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Type of leading change         &  Described in  \\
        \midrule
        High up change leaders or sponsors  &
                P3, P5, P24, P31, P36, P38, P46, P49  \\
        Agile task group foor coordinating change   &
                P4, P16, P18, P21, P23, P25, P30, P40, P41,
                P43, P45, P48, P49, P50  \\
        \bottomrule
    \end{tabular}
    \caption{Which entities were leading change in the agile transformation}
    \label{table:transformation_leadership}
\end{table}

@@

Many organizations formed an agile task force or similar entity for coordinating
and leading the change. It was typical that in the beginning of the
transformation, or when it had been acknowledged that the old model had
problems, a work group was founded for coordinating the changes to be done. The
change team usually consisted of management personnel [P43, P50], and was
reinforced with external agile consultants [P18, P21, P25, P30]. Some cases
highlighted that the team had a cross organizational staff who were familiar
with the varying functions that would be affected by changes [P4, P16, P21, P41,
P48]. It was important that theere was a group of people who were strongly
committed to making a change happen [P43].

The tasks of the change team included first finding an alternative delivery
method to solve problems in the old model [P21, P30]. During the transformation
the team stimulated agile adoption in the organization [P18, P45, P49]. Examples
on their tasks were informing people on the agile model [P4], educating and
coaching [P16, P45, P48, P49], creating an agile cookbook [P23], and organizing
presentations and workshops [P25, P41]. The change team also assessed the
success of transformed teams, and worked for repeating their success across the
organization [P16, P40, P41]. Still one characteristic was that the team was
empowered to act on impediments they discovered [P16, P50].

@@

% High up change leaders

In many cases it was described that the change was initiated by a limited number
of people in high-up positions. In these cases typical positions attributed for
giving the initial push for change were CxO's, vice presidents, and directors.
The pressence of a high up manager was described to underline the organization's
commitment for change [P24].

% Other change leaders

Some organizations looked for recruiting champions to push with the
transformation in local business units [P9].

An important factor in the transformation was that organizations needed people
to spread the word of the new methodology, and persuade for change [P9].

Who?

How were they selected?

What is their task?

What did they do?

Do they have challenges in their tasks?

What is particular?

@@

[P3] High up leader
* A Development Manager
* Who: A single person
* What: The team expressed a need to formalize their development process
* What: He was able to push a few other people to get interested in agile
* What: The word spread. There was some interest already before, but he helped ignite the spark

[P5] High up leader
* A VP joined, who was pro-agile
* Who: A vice president manager
* What: He started introducing agile to the company
* He kept firm and committed to the agile transformation --> Regardless of a few casualities

[P24] High up leader
* Who: The CTO
* What: He lead training and awareness sessions
* Particular: His presence made the management commitment to change clear

[P31] High up leader
* Who: A vice president
* What: Make the change happen, commitment
* What: Educating executive peers, be a guardian of the agile culture
* Particular: He was committed, and pushed for the change to happen

[P36] Consulting company
* The consulting company wanted to work in an agile way
* The contracting company got a view of agile practices, and a demonstration of effectivity
[P36] High up leader
* A pilot project was successful, and a high up manager became convinced
* Who: The director of IT
* What: He was the management champion. He would anticipate and deal with challenges

[P38] High up leader
* The company hired a new CTO, known for helping troubled companies
* Who: The new CTO
* What: He assessed the current problems
* What: He took steps for making people get interested in agile
* What: He had determination to make difficult management decisions for getting agile working
* What: Important role of persuading the rest of the business to change their way of working

[P46] High up leaders
* A new CIO was hired. Later a director was hired
* Who: The new CIO, another director
* What: CIO took attention to break down internal barriers, and make the company perform better
* What: CIO persuaded business partners
* What: Director: a vision of makin things work better, and making everyone proud of their work
* What: The director persuaded the development group
* What: The director stayed firm and committed, when presented with impediments

[P49] High up leader
* A grand experiment was started wit the lead of the CIO
* Who: the CIO
* What: Persuaded to do a transformation

[P18] Managers
* Managers are key in making change stick
* Who: Managers
* What: Lead people, make the change stick
* Particular: Managers needed to be coached for taking this leadership role

[P14] One manager
* There was one project manager who wanted to drive agile
* Who: One project manager
* What: He was devoted to use agile methods
* What: He fought for getting use of agile accepted

[P2] Group
* A group of agile advocates is driving the push
* Who: Advocates, coaches
* Task: facilitate successful agile adoption, spread knowledge
* Task: Persuade other staff to adopt
* Challenge: move agile from development teams to rest of the business

[P16] Group (more for ``change team'' ? )
* Who: A cross functional rollout team
* Who: People representing different roles
* What: Created a schedule for rollout, provided expertise, coaching
* What: Spreading the word
* What: Removal of obstacles

[P6] Champions in teams
* There were agile champions in teams
* Who: People in teams, from all disciplines
* What: They knew the problems at hand, and had the knowledge to adjust the process accordingly
* Particular: Hard to find people who understand the principles, and can help their teams

[P9] Champions, coaching staff, individuals in teams
* Champions were hired in business uints to help spread knowledge
* Who: People across the organization
* Who: Agile coaching staff was hiring people
* Task: Help spread agile knowledge, teach techniques
* Particular: The coaching staff was disbanded, as they could not produce results
* There were agile people in the trenches afterwards, who drove the agile use further

[P17] An evangelist
* It was seen as necessary to have an evangelist position when the scale became larger
* Who: someone who lead the Scrum of Scrums
* What: Coordinate work when it was obvious that coordination was needed

[P27] A single developer
* Who: A developer took the role of leading the team
* What: The team was empowered when there was an internal leader
